Graph Topology Learning from Binary Signals on Graph

### 2022-04-29 poster html copy/poster html.Rmd
fix logo

---
title: Graph Topology Learning from Binary Signals on Graph
author:
  - name: Skip Moses
  - name: Jing Guo
affiliation:
    address: Department of Mathematics and Statistics, California State University, Chico
column_numbers: 4
primary_colour: "#9D2235"
secondary_colour: "#FFFFFF"
poster_height: "36in"
poster_width: "60in"
logoright_name: pictures/DSI_Hexbin_sticker_01.png
#logoright_name: pictures/logo1.png
output: 
  posterdown::posterdown_html:
    self_contained: false
bibliography: ref.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

@@

Data often has  an underlying structure or geometry that can be modeled as a signal on the vertices of a weighted, undirected graph. Traditionally, the emphasis was on using a underlying graph, or network, to understand the properties of signals over the vertices. Recently, there has been a surge in converse problem; learning a graph structure from a set of signals satisfying some constraints [@dong2016learning] [ @ortega2018graph]. In previous research [@dong2016learning], [@tugnait2021sparse], and [@saboksayr2021accelerated], signals on graph were assumed to follow multivariate Gaussian distributions, but there has been little exploration in learning a network from binomial signals. In this work, we develop a novel methodology that allows for learning graph topology given a set of binary signals on the graph as shown in Figure \@ref(fig:GTG).

@@

 <body>      
        <p style="color:black;font-size:24px;">This work is supported by Research, Scholarship, and Creative Activity (RSCA) Award 2021-2022 through Chico State Enterprises. Thank you to Robin Donatello for approving this work for Data Science Capstone Project.</p>    
</body>

```{r , echo=FALSE,out.width="60%", out.height="10%",fig.show='hold',fig.align='center'}
knitr::include_graphics(c("pictures/logo1.png"))
```

>>>>

---
title: Graph Topology Learning from Binary Signals on Graph
author:
  - name: Skip Moses
  - name: Jing Guo
affiliation:
    address: Department of Mathematics and Statistics, California State University, Chico
column_numbers: 4
primary_colour: "#9D2235"
secondary_colour: "#FFFFFF"
poster_height: "36in"
poster_width: "60in"
logoright_name: pictures/DSI_Hexbin_sticker_01.png
logoleft_name: pictures/logo1.png
output: 
  posterdown::posterdown_html:
    self_contained: false
bibliography: ref.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
<style>
.poster_title {
  width: 50%;
  text-align: center;
  float: left;
  align-items: center;
  justify-content: center;
  padding: 30px;
  margin-top: 0.1in;
  margin-bottom: 0.1in;
}

.logo_left {
  width: 30%;
  display: flex;
  align-items: center;
  justify-content: center;
}

.logo_right {
  width: 9%;
  display: flex;
  align-items: center;
  justify-content: center;
}

</style>

@@

Data often has  an underlying structure or geometry that can be modeled as a signal on the vertices of a weighted, undirected graph. Traditionally, the emphasis was on using a underlying graph, or network, to understand the properties of signals over the vertices. Recently, there has been a surge in converse problem: learning a graph structure from a set of signals satisfying some constraints [@dong2016learning] [ @ortega2018graph]. In previous research [@dong2016learning], [@tugnait2021sparse], and [@saboksayr2021accelerated], signals on graph were assumed to follow multivariate Gaussian distributions, but there has been little exploration in learning a network from binomial signals. In this work, we develop a novel methodology that allows for learning graph topology given a set of binary signals on the graph as shown in Figure \@ref(fig:GTG).

@@

 <body>      
        <p style="color:black;font-size:32px;">This work is supported by Research, Scholarship, and Creative Activity (RSCA) Award 2021-2022 through Chico State Enterprises. Thank you to Robin Donatello for approving this work for Data Science Capstone Project.</p>    
</body>
